\section{Chapters summary}
In chapter~\ref{chap:about-x}, About X protocol,
we will not directly describe the project itself but rather give 
some general explanations about the X protocol, which the project is based on.
We will describe the fundamental concepts and the key notions of the protocol 
so that the reader can have a sufficient understanding of it to continue reading 
through this paper.

In chapter~\ref{chap:general-architecture}, General architecture, we will give a general overview of the 
project and its architecture. We will explain how the project is split, as well as the 
responsibilities of the different part of it.

In chapter~\ref{chap:server-frontend}, Server frontend application, we will explain 
how this part of the project is working, and explain more in detail what it is supposed to do 
and how. We will also be discussing about the login manager part of the application which is
handled in this application.

In chapter~\ref{chap:server-backend}, Server backend application, we will give 
more detailed of how the system is communicating with the X clients, and how the 
data received and sent to the X clients is handled.

In chapter~\ref{chap:browser-app}, Web browser application, we will describe
how the frontend roles of the X server, rendering and event handling, are handled and 
implemented. 

In chapter~\ref{chap:evaluation}, Evaluation, we will discuss about the general 
performances of the system, principally in a qualitative manner, and will also 
try to evaluate it from an end-user point of view.

In chapter~\ref{chap:related-work}, Related work, we will present two projects that 
are in some way related to this project and have some goals in common with it.